---
title: "Homework 1"
author: "Lydia Parr lcp2148"
date: 2019-09-29
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(tibble)
```

# Problem 1.

Creating a data frame with: 

* random sample of size 10 from a standard Normal distribution

* logical vector indicating whether elements of the sample are greater than 0

* character vector of length 10

* factor vector of length 10, with 3 different factor “levels”

```{r data_frame}

hw1_df = tibble(
  norm_samp = rnorm(10, mean = 0), 
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_logical = norm_samp > 0,
  vec_factor = (c("low", "low", "low", "med", "med", "med", "med", "high", "high", "high")) 
)

```


Trying to take mean of each variables in the dataframe. 

```{r means}

mean_samp = mean(pull(hw1_df, norm_samp))

mean_char = mean(pull(hw1_df, vec_char))

mean_logic = mean(pull(hw1_df, vec_logical))

mean_facto = mean(pull(hw1_df, vec_factor))
```

There are errors for the variables without numerical values, because you cannot take the mean. 

The mean for the random sample is `mean_samp = mean(pull(hw1_df, norm_samp))` = 0.128

The mean for the logical vector indicating whether elements of the sample are greater than 0 `mean_logic = mean(pull(hw1_df, vec_logical))` = 0.700


In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

