---
title: "Homework 1"
author: "Lydia Parr lcp2148"
date: 2019-09-29
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(tibble)
```

# Problem 1.

Creating a data frame with: 

* random sample of size 10 from a standard Normal distribution

* logical vector indicating whether elements of the sample are greater than 0

* character vector of length 10

* factor vector of length 10, with 3 different factor “levels”

```{r data_frame}

hw1_df = tibble(
  norm_samp = rnorm(10, mean = 0), 
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_logical = ifelse(norm_samp > 0, print("Negative"), print("Not")),
  vec_factor = (c("low", "low", "low", "med", "med", "med", "med", "high", "high", "high")) 
)

```


Trying to take mean of each variables in the dataframe. 

```{r means}

mean_samp = mean(pull(hw1_df, norm_samp))

mean_char = mean(pull(hw1_df, vec_char))

mean_logic = mean(pull(hw1_df, vec_logical))

mean_facto = mean(pull(hw1_df, vec_factor))
```

There are errors for the variables without numerical values, because you cannot take the mean. 

The mean for the random sample is `mean_samp = mean(pull(hw1_df, norm_samp))` = 0.128

Next, I'll try to apply the as.numeric function to the variables which couldn't give a mean. 

```{r numeric}

vec_char = as.numeric(pull(hw1_df,vec_char))

vec_logical = as.numeric(pull(hw1_df,vec_logical))

vec_factor = as.numeric(pull(hw1_df,vec_factor))

```

Running this code returns the "NAs introduced by coercion" warning, because none of the variable values were equivalent to a numerical one. This would make calculating the mean from these three variables impossible. 

# Problem 2.
